%PARA CITAR \cite{LO QUE DICE ADENTRO DE BIBITEM}
\begin{thebibliography}{9}
    \bibitem{paperezpeleta} 
    J. Ezpeleta, J. M. Colom and J. Martinez.A Petri net based deadlock prevention policy for flexible manufacturing systems, in IEEE Transactions on Robotics and Automation, vol. 11, no. 2, pp. 173-184, April 1995, DOI: 10.1109/70.370500.
 
    \bibitem{paperezpeletav2} 
    Zhong, C.‐F. and Li and Z.‐W.
    \textit{Design of liveness‐enforcing supervisors via transforming plant petri net models of FMS. Asian Journal of Control, vol. 12: 240-252. 2010. DOI: 10.1002/asjc.182}.
 
    \bibitem{paperguanjun} 
    G. Liu, C. Jiang and M. Zhou.
    \textit{Two Simple Deadlock Prevention Policies for S³PR Based on Key-Resource/Operation-Place Pairs, in IEEE Transactions on Automation Science and Engineering, vol. 7, no. 4, pp. 945-957, Oct. 2010, DOI: 10.1109/TASE.2010.2050059}.
    
    \bibitem{paperhospital} 
    Timotei, A. and Colom, J.
    \textit{A New Approach to Prevent Deadlock in S3PR Nets with Unreplicable Resources.In Proceedings of the 2nd International Conference on Operations Research and Enterprise Systems - vol. 1: ICORES, ISBN 978-989-8565-40-2, pages 252-257. 2013. DOI: 10.5220/0004275702520257}.
    
    \bibitem{paperhuang} 
    Huang, Yi-Sheng \& Pan, Yen-Liang \& Su, Pin-June.
    \textit{Transition-Based Deadlock Detection and Recovery Policy for FMSs Using Graph Technique. ACM Transactions on Embedded Computing Systems. vol. 12. 2012. DOI: 10.1145/2406336.2406347}.
    
    \bibitem{papermfc} 
    Abdul-Hussin M.H.
    \textit{On Structural Conditions of S3PR based Siphon to Prevent Deadlocks of Manufacturing Systems, International Journal of  Simulation, Systems, Science. \& Technology, (IJSSST), vol. 17, no. 33, pp. 32.1-32.8, 2016. DOI: 10.5013/IJSSST.a.17.33.32}.
    
    \bibitem{paperportugal} 
    S. Wang, C. Wang and M. Zhou.
    \textit{Optimal siphon-based deadlock prevention policy for a class of Petri nets in automation. IEEE International Conference on Systems, Man, and Cybernetics, Anchorage, AK, 2011, pp. 826-831. 2011. DOI: 10.1109/ICSMC.2011.6083755.}.
    
    \bibitem{paperzhao} 
    Zhao, Mi \& Hou, Yifan.
    \textit{An iterative method for synthesizing non-blocking supervisors for a class of generalized Petri nets using mathematical programming. Discrete Event Dynamic Systems. vol. 23. 2013. DOI: 10.1007/s10626-011-0124-9}.
    
    \bibitem{libro1} 
    M. V. Iordache and P. J. Antsaklis.
    \textit{Concurrent program synthesis based on supervisory control, Proceedings of the 2010 American Control Conference, Baltimore, MD, 2010, pp. 3378-3383, DOI: 10.1109/ACC.2010.5530904}.
    
    \bibitem{libropopn} 
    Naiqi Wu - MengChu Zhou.
    \textit{System modeling and Control with Resource-Oriented Petri Nets}.
    
    \bibitem{paperpanama} 
    Kezić, Danko \& Peric, Nedjeljko \& Petrovic, Ivan.An Algorithm for Deadlock Prevention Based on Iterative Siphon Control of Petri Net. AUTOMATIKA: Journal for Control, Measurement, Electronics, Computing and Communications. vol.47 No.1-2. 2006.
    
    \bibitem{petrinator} 
    Joaquín Rodríguez Felici, Leandro José Assón. 
    \textit{Editor, Simulador y Analizador de Redes de Petri}. 2017.
    
    \bibitem{libro2} 
    Zhi Wu Li \& Meng Chu Zhou.
    \textit{Deadlock Resolution in Automated Manufacturing Systems - A novel Petri Net Approach. Springer Publishing Company, Incorporated. 2009. DOI: 10.1007/978-1-84882-244-3}.

\end{thebibliography}